### 2025-03-06 README.Rmd
Fix install instructions (eval=FALSE)

<!-- badges: start -->
[![R-CMD-check](https://github.com/bmait101/hatchR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/bmait101/hatchR/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

@@

Install and load the most recent approved version from CRAN by running:

```{r}
# install the most recent approved version from CRAN
install.packages("hatchR")
```

Install the development version of **hatchR** from [GitHub](https://github.com/) by running:

```{r}
# install the most recent version from GitHub
pak::pak("bmait101/hatchR")
```

>>>>

<!-- badges: start -->
[![R-CMD-check](https://github.com/bmait101/hatchR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/bmait101/hatchR/actions/workflows/R-CMD-check.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/hatchR)](https://CRAN.R-project.org/package=hatchR)
[![cran checks](https://badges.cranchecks.info/worst/hatchR.svg)](https://cran.r-project.org/web/checks/check_results_hatchR.html)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
<!-- badges: end -->

@@

Install the released version from CRAN:

```{r, eval = FALSE}
install.packages("hatchR")
```

Install the development version of **hatchR** from GitHub:

```{r, eval = FALSE}
# install.packages("pak")
pak::pak("bmait101/hatchR")
```
